Analysis of CSV File Reading in R

### 2021-12-10 paper.Rmd
last paper fix before completely transition to Overleaf

The response variable, $y_{ijkl}$, indicates the speed time in seconds corresponding to each run conducted in the experiment. Here $\mu$ represents the overall mean reading time,  and $\alpha_i$, $\beta_j$, and $\gamma_k$ are the main effects of three factors file size, computer device, and `R` function/package. There are also 3 two-factor and 1 three-factor interaction effects in our model. In addition, this model includes an error component $\epsilon_{ijkl}$, and the assumptions for the residuals are that they are normally distributed and the variance is constant across the groups.

>>>>

The response variable, $y_{ijkl}$, indicates the speed time in seconds corresponding to each run conducted in the experiment. Here $\mu$ represents the overall mean reading time,  and $\tau_i$, $\beta_j$, and $\gamma_k$ are the main effects of three factors file size, computer device, and `R` function/package. There are also 3 two-factor and 1 three-factor interaction effects in our model. In addition, this model includes an error component $\epsilon_{ijkl}$, and the assumptions for the residuals are that they are normally distributed and the variance is constant across the groups.
